---
title: "Final Project"
author: "Taylor Nguyen"
format:
  html:
    theme: yeti
---

The sauces dataset involves Hot Ones sauces that have been tried over the 21 seasons and their Scoville Heat Units. It includes information on different sauces used every season, the sauce number per season (out of 10 sauces per season), the number of seasons of Hot Ones, and the Scoville of each sauce. The dataset derives from R for Data Science Online Learning Community via the Tidy Tuesday project.

```{r}
#| echo: FALSE
#| message: FALSE
library(tidyverse)
library(gtsummary)
library(broom)
```

```{r}
#| echo: FALSE
sauces <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-08-08/sauces.csv")
```

# Customization of `tbl_summary()`
```{r}
#| echo: FALSE
#| message: FALSE
#| label: tbl-one
#| tbl-cap: "This is a table of Hot Ones sauces over the seasons"

sauces_col <- c("season", "sauce_number", "sauce_name", "scoville")
sauces <- read_csv(here::here("data/raw/sauces.csv"),
									 skip = 1, col_names = sauces_col) |>
	mutate(sauce_number = factor(sauce_number, labels = (1:10)),
				 season = factor(season, labels = c("Season 1", "Season 2", "Season 3", "Season 4", "Season 5",
				 																	  "Season 6", "Season 7", "Season 8", "Season 9", "Season 10",
				 																	  "Season 11", "Season 12", "Season 13", "Season 14", "Season 15",
				 																	  "Season 16", "Season 17", "Season 18", "Season 19", "Season 20",
				 																	  "Season 21")))

table1 <- tbl_summary(
	sauces,
	by = season,
	include = c(season, sauce_number, sauce_name, scoville),
	label = list(
		sauce_number ~ "Sauce Number",
		sauce_name ~ "Sauce Name",
		scoville ~ "Scoville"
	),
	missing_text = "Missing")
table1
```

@tbl-one looks at different sauces used for each Hot Ones season and their Scoville Heat Unit.

```{r}
#| echo: FALSE
#| label: fig-hist
#| fig-cap: "This is a histogram of Hot Ones sauces"
hist(sauces$scoville)
```

@fig-hist is a histogram of the distribution of Scoville Heat Units in the sauces dataset.

@fig-hist contains a histogram of Scoville Heat Units for the sauces dataset and @tbl-one is a table of Hot Ones sauces over the seasons and their Scoville Heat Unit.

```{r}
#| echo: FALSE
scoville_szn1 <- inline_text(table1, variable = "scoville", 
                        						 column = "Season 1")
scoville_szn2 <- inline_text(table1, variable = "scoville", 
                        						 column = "Season 2")
```

A greater proportion of Season 2 (`r scoville_szn2`) than Season 1 (`r scoville_szn1`) had more Scoville Heat Units.

There were `r 200 + 10` sauces over the Hot Ones seasons.

```{r}
#| echo: FALSE
scoville_avg <- mean(sauces$scoville, na.rm = TRUE)
```

The average amount of scoville was `r scoville_avg`

```{r}
#| echo: FALSE
stats <- list(n = nrow(sauces), scoville_avg = mean(sauces$scoville))
```

There were `r stats$n` sauces with a mean Scoville of `r stats$scoville_avg`.

```{r}
inline_text(table1, variable = "scoville", column = "Season 12")
```

Season 12 had a median Scoville Heat Unit of 60,500.

# Univariate Regression
```{r}
#| echo: FALSE
#| label: tbl-two
#| tbl-cap: "This is a univariate regression of Scoville by Season, Sauce Number, and Sauce Name"
regress1 <- tbl_uvregression(
	sauces,
	y = scoville,
	include = c(season, sauce_number, sauce_name, scoville),
	method = lm)
regress1
```

@tbl-two is a univariate regression with scoville as the dependent variable.

# Multivariable Regression
```{r}
#| echo: FALSE
linear_model <- lm(scoville ~ season + sauce_number + sauce_name,
									 data = sauces)
```

```{r}
#| echo: FALSE
linear_model_int <- lm(scoville ~ season*sauce_number + sauce_name,
											 data = sauces)
```

```{r}
#| echo: FALSE
#| label: tbl-three
#| tbl-cap: "This is a multivariable regression of Scoville by Season, Sauce Number, and Sauce Name"
regress2 <- tbl_regression(
	linear_model,
	intercept = TRUE,
	label = list(
		season ~ "Season",
		sauce_number ~ "Sauce Number",
		sauce_name ~ "Sauce Name"
	))
regress2
```

@tbl-three is a multivariable regression table produced from the linear_model function.

```{r}
#| echo: FALSE
#| warning: FALSE
tbl_no_int <- tbl_regression(
	linear_model,
	intercept = TRUE,
	label = list(
		season ~ "Season",
		sauce_number ~ "Sauce Number",
		sauce_name ~ "Sauce Name"
	))

tbl_int <- tbl_regression(
	linear_model_int,
	intercept = TRUE,
	label = list(
		season ~ "Season",
		sauce_number ~ "Sauce Number",
		sauce_name ~ "Sauce Name",
		`season:sauce_number` ~ "Season/Sauce Number interaction"
	))
```

```{r}
#| echo: FALSE
#| label: tbl-four
#| tbl-cap: "This is a merged multivariable regression table of Scoville by Season, Sauce Number, and Sauce Name"
regress3 <- tbl_merge(list(tbl_no_int, tbl_int), 
          tab_spanner = c("**Model 1**", "**Model 2**"))
regress3
```

@tbl-four is a multivariable regression table comparing a model with and without interaction between the variables.

